### 2021-01-12 LaTeX-USENIX/sections/paper.tex
done for now
Done with edits + added the Arbitrum to the repo

The main research question is how many orders can be processed in a single Ethereum transaction when closing the call market, using Ethereum today. As our previous experiments indicated, the choice of priority queue (PQ) implementation is the main influence on performance (see Table~\ref{tab:worst_case_matching}). We implemented a generic call market that interfaces with a generic PQ (at its own contract address) and ran experiments for each PQ implementation. We looked at the \textit{worst-case} for performance which is when every submitted bid and ask is marketable (\ie will require fulfillment). In the first two columns, we determine the highest number of orders that can be processed in a single call to the \texttt{closeMarket()} and not exceed the the current Ethereum block gas limit of 11,741,495. Since Ethereum will become more efficient over time, we also were interested in how much gas it would cost to execute 1000 pairs of orders which is given in the third column. The fourth column indicates the cost of submitting a bid or ask --- since this costs will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.

@@

\item \textbf{Store the mapping in a separate DApp.} We could wrap the mapping inside its own DApp and when we are done with the mapping, we can run \texttt{SELFDESTRUCT} on the contract. This refunds us 24,000 gas which is less than the cost of deploying the extra contract. Additionally, every call to the mapping is more expensive because (1) it is an external function call, and (2) the calls need access control to ensure only the market contract can write to it (if a mapping is a local variable, you get private access for free).

@@

As miners are paid all price improvements in the market, it is possible that a miner might run \texttt{closeMarket()} and it would pay for itself. However we consider two other scenarios that do not assume miners can automatically find MEV opportunities. One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time until the order book is empty (this is sensible design in any case to safeguard against the orderbook from locking up because the number of orders exceeds the gas limit to process them).  Once the time window for submitting orders is past, a new market is created (without settling the previous market). Every order submission on the new market also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market. This solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second related issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).

@@

Imagine you have just launched a standard token on Ethereum. Now want your holders to be able to trade it. While the barrier to entry for exchange services is low, it still exists. For a centralized or decentralized exchange, you have to convince the operators to list your token and you will be delayed while they process your request. For an automated market maker, you will have to lock up a large amount of ETH into the DApp, along with your tokens. For rollups, you will have to host your own servers. By contrast to all of these, with an on-chain orderbook, you just deploy the code alongside your token and trading is immediately supported. This should concern regulators. Even if it is too slow today, there is little reason for developers not to offer it as a fallback solution that accompanies every token. With future improvements to blockchain scalability, it could become the defacto trading method.

>>>>

The main research question is how many orders can be processed in a single Ethereum transaction when closing the call market, using Ethereum today. As our previous experiments indicated, the choice of PQ implementation is the main influence on performance (see Table~\ref{tab:worst_case_matching}). We implemented a generic call market that interfaces with a generic PQ (at its own contract address) and ran experiments for each PQ implementation. We looked at the \textit{worst-case} for performance which is when every submitted bid and ask is marketable (\ie will require fulfillment). In the first two columns, we determine the highest number of orders that can be processed in a single call to the \texttt{closeMarket()} and not exceed the the current Ethereum block gas limit of 11,741,495. Since Ethereum will become more efficient over time, we also were interested in how much gas it would cost to execute 1000 pairs of orders which is given in the third column. The fourth column indicates the cost of submitting a bid or ask --- since this costs will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.

@@

\item \textbf{Store the Mapping in a Separate DApp.} We could wrap the mapping inside its own DApp and when we are done with the mapping, we can run \texttt{SELFDESTRUCT} on the contract. This refunds us 24,000 gas which is less than the cost of deploying the extra contract. Additionally, every call to the mapping is more expensive because (1) it is an external function call, and (2) the calls need access control to ensure only the market contract can write to it (if a mapping is a local variable, you get private access for free).

@@

As miners are paid all price improvements in the market, it is possible that a miner might run \texttt{closeMarket()} and it would pay for itself. However we consider two other scenarios that do not assume miners can automatically find MEV opportunities. One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time until the order book is empty (this is sensible design in any case to safeguard against the order book from locking up because the number of orders exceeds the gas limit to process them).  Once the time window for submitting orders is past, a new market is created (without settling the previous market). Every order submission on the new market also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market. This solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second related issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).

@@

Imagine you have just launched a token on Ethereum. Now want to be able to trade it. While the barrier to entry for exchange services is low, it still exists. For a centralized or decentralized exchange, you have to convince the operators to list your token and you will be delayed while they process your request. For an automated market maker, you will have to lock up a large amount of ETH into the DApp, along with your tokens. For rollups, you will have to host your own servers. By contrast to all of these, with an on-chain order book, you just deploy the code alongside your token and trading is immediately supported. This should concern regulators. Even if it is too slow today, there is little reason for developers not to offer it as a fallback solution that accompanies every token. With future improvements to blockchain scalability, it could become the defacto trading method.
